### 2023-10-06 vesicle_code/docs/confinedMulti/response.tex

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{url}

\newcommand{\subfigimg}[3][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{0pt}\raisebox{\dimexpr\ht1-0\baselineskip}{\bf
  \normalsize #2}}% Print label
  \phantom{\usebox1}% Insert appropriate spacing
}

@@

%%%%%%%%
\item The authors mention the phrase `size of lubrication layer' in the
  paper. They need to explicitly define this parameter. It could be
    confusing to a reader whether they talk about
    $|\gamma_{\mathrm{layer}}|$ or $w_{\mathrm{top}}$ and
    $w_{\mathrm{bottom}}$.

\noindent
    {\bf Response:} We have labelled $w_{\mathrm{top}}$ and
    $w_{\mathrm{bot}}$ in Figure 1. We have adjusted the text in Section
    2.4.

%%%%%%%%
\item The authors measure the tangential velocity at 4 points. They
  should provide some justification for this number. Also, it is
    advisable that in Figure 7, the authors use a different color for
    each velocity plot. The plot looks highly convoluted and does not
    convey the message clearly. Also, what are the bounds within which
    the authors call the tangential velocity to be constant in Figure 7?
    They should define a bound for the variation that could be
    considered constant. Moreover, in Figure 7, for the floppy vesicle,
    the authors see a large deviation for the tangential velocity. It
    doesn't seem like the velocity could be called `constant'. The
    authors should provide a more detailed explanation for this.

\noindent
    {\bf Response:} We calculated the tangential velocity of all $N =
    1024$ Lagrangian points for each of the three cases. Plotting all
    1024 lines in the manuscript we be uninformative. To prove this is
    the case, a plot of 32 of the tangential velocities is in
    Figure~\ref{fig:tangVel} of this document. Instead, in the document,
    we report the average tangential velocity in the region $x \in
    [4,10]$, and the report the spread of all tangential velocities from
    this mean value. If this spread is less than 15\%, we would
    characterize this as a tank-treading vesicle. There spread is 1.2\%
    for the stiff single-component vesicle, 12\% for the multicomponent
    case, and 313\% for the floppy single-component case. Therefore, the
    floppy single-component vesicle is not tank-treading, while the
    other two cases are tank-treading. We have made this clear in the
    text.
    {\bf TODO: Change color of Fig 7 lines or state why we don't do
    this.}

\begin{figure}[ht]
  \centering
  \subfigimg[width=0.3\textwidth]{(a)}{figures/SC_treading_velocity_review.pdf}
  \subfigimg[width=0.3\textwidth]{(b)}{figures/SCp55_treading_velocity_review.pdf}
  \subfigimg[width=0.3\textwidth]{(c)}{figures/MCp5_treading_velocity_review.pdf}
  \caption{\label{fig:tangVel} The tangential velocity of 32 points of
  the (a) stiff single-component vesicle, (b) floppy single-component
  vesicle, (c) multicomponent vesicle.}
\end{figure}

### 2023-10-06 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on revisions

The vesicle and solid walls are discretized at a set of collocation
points. The single-layer potential is approximated using quadrature for
weakly-singular integrands, while the double-layer potential is
approximated using the spectrally accurate trapezoid rule. A high-order
quadrature method resolves the hydrodynamic interactions between the
vesicle and the solid wall~\cite{qua-bir2014}. Arclength derivatives are
computed with spectral accuracy using Fourier methods. The resulting
linear system is solved using GMRES. Finally, time stepping is carried
out using the second-order Adams-Bashforth method.

@@

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. The bottom of
Figure~\ref{fig:lubricationComposite} shows the tank-treading velocities
of four Lagrangian points. The inset shows the vesicle configuration in
the closely-fitting part of the channel, the black dashed line is the
center line of the channel, the marks are the four Lagrangian points,
and the rounded arrow denotes the direction of rotation. The stiff
single-component and multicomponent vesicles are clearly tank treading.
The direction and speed of the tank-treading depends on how much of
the vesicle membrane is exposed to positive shear (below the center
line) versus how much is exposed to negative shear (above the center
line) \cite{kao-bir-mis2009}. The majority of the membrane of the stiff single-component and
multicomponent vesicles are below the center line, and this results in a
clockwise tank-treading behavior. In contrast, the majority of the
membrane of the floppy single-component vesicle is above the center
line, and the result is counterclockwise tank-treading. In addition, the
tank-treading velocity can be correlated to the percentage of its
membrane that is below the center line. We note, however, that the
floppy single-component vesicle is still undergoing deformations, so the
tangential velocities have not converged to a fixed value.

>>>>

The vesicle and solid walls are discretized at a set of 
\textcolor{blue}{
$N$ and $N_{\mathrm{wall}}$
}
collocation points,
\textcolor{blue}{
respectively.}
The single-layer potential is approximated using quadrature for
weakly-singular integrands, while the double-layer potential is
approximated using the spectrally accurate trapezoid rule. A high-order
quadrature method resolves the hydrodynamic interactions between the
vesicle and the solid wall~\cite{qua-bir2014}. Arclength derivatives are
computed with spectral accuracy using Fourier methods. The resulting
linear system is solved using GMRES. Finally, time stepping is carried
out using the second-order Adams-Bashforth method.

@@

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. The bottom of
Figure~\ref{fig:lubricationComposite} shows the 
\textcolor{blue}{
tangential
}
%tank-treading
velocities of four Lagrangian points. The inset shows the vesicle
configuration in the closely-fitting part of the channel, the black
dashed line is the center line of the channel, the marks are the four
Lagrangian points, and the rounded arrow denotes the direction of
rotation. 
\textcolor{blue}
{
To determine if a vesicle is tank-treading, we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the maximum and minimum tangential velocities are within
15\% of the average tangential velocity, we characterize the vesicle as
tank-treading. The average tangential velocities are $-1.00 \times
10^{-1}$ for the stiff single-component vesicle, $3.31 \times 10^{-2}$
for the floppy single-component vesicle, and $-8.48 \times 10^{-1}$ for
the multicomponent vesicle. The spread of the maximum and minimum
velocities from these average tangential velocities are $1.2\%$ for the
stiff single-component vesicle, $12\%$ for the multicomponent vesicle,
and over $300\%$ for the floppy single-component vesicle. Therefore, we
classify the stiff single-component and multicomponent vesicles as tank
treading, while the floppy single-component is not tank treading.
}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, the vesicle dynamics are not tank-treading as the
vesicle is undergoing large normal deformations.
}
%tank-treading. 
\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.
